Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean (*Phaseolus vulgaris*) in the United States

### 2017-10-31 doc/manuscript/manuscript.Rmd
update title; add citation to first sentence; address #15

---
title: Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States
preprint: false
author:
  - name: Zhian N. Kamvar
    email: zkamvar@unl.edu
    affiliation: 1
  - name: Bimal Sajeewa Amaradasa
    email: bamaradasa@ufl.edu
    affiliation: 1
  - name: Rachana Jhala
    email: rjhala2@unl.edu
    affiliation: 1
  - name: Serena McCoy
    email: serena.mccoy@icloud.com
    affiliation: 1
  - name: James Steadman
    email: jsteadman1@unl.edu
    affiliation: 1
  - name: Sydney E. Everhart
    email: everhart@unl.edu
    affiliation: 1
    corresponding: true
affiliation:
  - code: 1
    address: Department of Plant Pathology, University of Nebraska-Lincoln, Lincoln, NE 68583
abstract: >
  `r paste(readLines("abstract.md"), collapse = "\n  ")`
header-includes: |
  \usepackage{indentfirst}

@@

*Sclerotinia sclerotiorum* (Lib.) de Bary is an ascomycete plant pathogen with a worldwide distribution.
This is a necrotrophic pathogen that is primarily homothallic (self-fertilization) and has the ability to survive for more than five years in soil using melanized survival structures called sclerotia [@bolton2006sclerotinia; @sexton2006population]. 
It causes disease on more than 400 plant species belonging to 75 families [@boland1994index] including crops of major economic importance such as sunflower (*Helianthus spp.*), soybean (*Glycine max* L.), canola (*Brassica napa* L., *Brassica campestris* L.), and dry bean (*Phaseolus vulgaris* L.) [@bolton2006sclerotinia]. 
On dry bean, *S. sclerotiorum* is the causal agent of white mold, a devastating disease that can be yield-limiting in temperate climates [@steadman1983white].

>>>>

---
title: Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean (*Phaseolus vulgaris*) in the United States
preprint: false
author:
  - name: Zhian N. Kamvar
    email: zkamvar@unl.edu
    affiliation: 1
  - name: Bimal Sajeewa Amaradasa
    email: b.amaradasa@ufl.edu
    affiliation: 1
  - name: Rachana Jhala
    email: rjhala2@unl.edu
    affiliation: 1
  - name: Serena McCoy
    email: serena.mccoy@icloud.com
    affiliation: 1
  - name: James Steadman
    email: jsteadman1@unl.edu
    affiliation: 1
  - name: Sydney E. Everhart
    email: everhart@unl.edu
    affiliation: 1
    corresponding: true
affiliation:
  - code: 1
    address: Department of Plant Pathology, University of Nebraska-Lincoln, Lincoln, NE 68583
abstract: >
  `r paste(readLines("abstract.md"), collapse = "\n  ")`
header-includes: |
  \usepackage{indentfirst}

@@

*Sclerotinia sclerotiorum* (Lib.) de Bary is an ascomycete plant pathogen with a worldwide distribution [@bolton2006sclerotinia].
This is a necrotrophic pathogen that is primarily homothallic (self-fertilization) and has the ability to survive for more than five years in soil using melanized survival structures called sclerotia [@bolton2006sclerotinia; @sexton2006population]. 
It causes disease on more than 400 plant species belonging to 75 families [@boland1994index] including crops of major economic importance such as sunflower (*Helianthus spp.*), soybean (*Glycine max* L.), canola (*Brassica napa* L., *Brassica campestris* L.), and dry bean (*Phaseolus vulgaris* L.) [@bolton2006sclerotinia]. 
On dry bean, *S. sclerotiorum* is the causal agent of white mold, a devastating disease that can be yield-limiting in temperate climates [@steadman1983white].
